### 2014-04-30 Rcode/intro.rmd
corrected bug in intro.rmd

#This code mostly borrowed from the examples in mixFdr in R help
m=beta.mfdr.J15
mTrue = list(pi=c(0.8,0.2),mu=c(0,0),sig=c(1,2))
par(mfcol=c(1,1))
s = seq(-5,5,by=0.01)
trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.002) # this tells it which indices to consider null
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))
 lines(s, fdrCurve, col = 2)
points(ss$betahat,beta.ash$localfdr,col=3)
points(ss$betahat,beta.ash.u$localfdr,col=4)
points(ss$betahat,beta.ash.hu$localfdr,col=5)

>>>>

#This code mostly borrowed from the examples in mixFdr in R help
m=beta.mfdr.J15
mTrue = list(pi=c(0.8,0.2),mu=c(0,0),sig=c(1,sqrt(5)))
par(mfcol=c(1,1))
s = seq(-5,5,by=0.01)
trueFdr = fdrMixModel(s,mTrue,c(TRUE,FALSE))
fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.002) # this tells it which indices to consider null
 plot(s, trueFdr, t = 'l', main = "fdr - Black is true", xlab = "z", ylab = "fdr", ylim = c(0,1))
 lines(s, fdrCurve, col = 2)
points(ss$betahat,beta.ash$localfdr,col=3)
points(ss$betahat,beta.ash.u$localfdr,col=4)
points(ss$betahat,beta.ash.hu$localfdr,col=5)
